Modeling HEPES buffer with a charge-balance approach

### 2023-12-08 noise.Rmd
See if estimation error depends on pKa/pH vicinity

>>>>

Does the estimation error depend on the vicinity between the observed
$\mathrm{pH}$ and the true value of $\mathrm{p}K_a$?

```{r, fig.height = 8}
source('definitions.R')
kw <- 1e-14
HEPTOT <- 0.05
nw <- cbind(nw, vicinity = t(mapply(
	function(pK_true, n_points) {
		SID <- seq(-5e-2, 4e-2, n_points)
		pK_true - mean(pHm(
			SID, HEPTOT, pK_true[1], pK_true[2], pK_true[3]
		))
	}, nw$pK_true, nw$n_points
)))
p1 <- xyplot(
	sqrt(pK1) ~ vicinity.1,
	aggregate(
		cbind(nw[c('pK1')]^2, nw['vicinity.1']),
		nw[c('noise_ratio','n_points','noise_kind','idx')],
		mean
	),
	subset = n_points <= 100 & noise_ratio <= 1e-2,
	group = paste(noise_ratio, n_points, noise_kind),
	scales = list(y = list(log = 10)),
	xlab = quote(pK[1]^'true' - mean(pH)),
	ylab = quote(sigma(pK[1]))
)
p2 <- xyplot(
	sqrt(pK2) ~ vicinity.2,
	aggregate(
		cbind(nw[c('pK2')]^2, nw['vicinity.2']),
		nw[c('noise_ratio','n_points','noise_kind','idx')],
		mean
	),
	subset = n_points <= 100 & noise_ratio <= 1e-2,
	group = paste(noise_ratio, n_points, noise_kind),
	scales = list(y = list(log = 10)),
	xlab = quote(pK[2]^'true' - mean(pH)),
	ylab = quote(sigma(pK[2]))
)
p3 <- xyplot(
	sqrt(pK3) ~ vicinity.3,
	aggregate(
		cbind(nw[c('pK3')]^2, nw['vicinity.3']),
		nw[c('noise_ratio','n_points','noise_kind','idx')],
		mean
	),
	subset = n_points <= 100 & noise_ratio <= 1e-2,
	group = paste(noise_ratio, n_points, noise_kind),
	scales = list(y = list(log = 10)),
	xlab = quote(pK[3]^'true' - mean(pH)),
	ylab = quote(sigma(pK[3]))
)
print(p1, split = c(1, 1, 1, 3), more = TRUE)
print(p2, split = c(1, 2, 1, 3), more = TRUE)
print(p3, split = c(1, 3, 1, 3))
```

It's very hard to see a pattern, and we have too much variability in
kinds of noise and not enough variability in true $\mathrm{p}K_a$
values, but it seems that if the true value of $\mathrm{p}K_a$ exceeds
the $\mathrm{pH}$ value on average, it can be reliably estimated.
